### 2024-02-15 documentation/thesis/thesis_document.tex
.

This makes it easy to integrate your own measuring devices into the
\gls{mrp} ecosystem at a later date. This is only possible with a
minimal functional hardware and firmware setup and was developed for
this purpose first.

@@

Each sensor that has been loaded with the firmware, registeres on to the
host \gls{pc} as a serial interface. There are several ways for the user
to interact with the sensor:

@@

Two functional sensor platforms
\ref{Build_sensors_with_different_capabilities.csv} were built in order
to create a solid test platform for later tests and for the development
of the \gls{mrp} \ref{software-readout-framework}-library with the
previously developed sensor concepts.

@@

Since the \emph{MMC5603NJ} only has limited measurement range of total
6uT, even small coin sized neodymium magnets already saturates the
sensor. It is possible to mount 3D printed spacers over the sensor to
increase the distance between the magnet and the sensor and thus also
measure these magnets.

@@

Another option is a custom interface board between the meter and the PC.
This is a good option as many modern \gls{pc}s or \gls{sbc}s no longer
offer an physical \emph{RS232} interface. As with the other sensors,
this interface consists of your \emph{Raspberry-Pi Pico} with an
additional level shifter.

The teslameter is connected to the microcontroller using two free
\gls{gpio}s in \gls{uart} mode. The firmware was adapted using a
separate build configuration. In order to be able to read and correctly
interpret the data from the microcontoller, the serial protocol of the
sensor was implemented in a customised version of the
\emph{CustomSensor} class \ref{lst:CustomSensorClass}.

@@

The software readout framework is the central software component that
was developed as part of this work. This software framework is intended
to provide a user-oriented data acquisition and analysis environment.
For this purpose, typical individual steps that occur in relation to
these tasks were implemented:

@@

All these possible task parts were divided into different blocks and
users were given the possibility of adding their own functionalities.

@@

For this purpose, the library was divided into individual modules, which
are shown in the graphic
\ref{MRP_library_module_high_level_overview.png}. In combination, these
represent a typical measurement-analysis-evaluation workflow of data.
For this purpose, a module system with standardised functional patterns
and data types was developed and packed together in a extendable Python
library.

@@

In order to realise the concept of user interaction points, the library
was divided into different modules. These modules can be divided into
two main categories:

@@

An important aspect is data import and export. On the one hand, this
allows the library to reuse and archive the measurements. On the other
hand, the focus during development was that it is also possible to use
the data in other programs.

@@

Taking these points into account, the \gls{json} format was chosen. This
is human and machine readable and there is a compatible parser for
almost every programming language.

The following code snippet \ref{lst:json_export_format_example} shows
the \gls{json} structure which is generated when a measurement thatt
using the library is exported. Here you can see that by using the
\gls{json} format, all measurement points and metadata are available in
readable plain text.

@@

To realize this, a \gls{lut} was created in the previous steps, which
contains information regarding \emph{requested capability}
-\textgreater{} \emph{sensor}-\gls{uuid} -\textgreater{} \emph{physical
sensor} and allows the commands to be routed.

@@

After generating simple measurements with random values in the previous
example \ref{mrpreading}, the next step is to record real sensor data.
For this purpose, the \emph{MRPHal} module was developed, which can
interact with all \emph{Unified Sensor} \ref{unified-sensor}-compatible
sensors. In the following example \ref{lst:mrpexample_hal}, an \emph{1D:
Single Sensor} \ref{d-single-sensor} is connected locally to the host
\gls{pc}.

@@

Although such examples are provided in the documentation, it must be
possible for programming beginners in particular to use them. To
simplify these tasks, a \gls{cli}
\ref{Example_measurement_analysis_pipeline.png} was implemented. The
libaray \gls{cli} implements the following functionalities:

@@

For this purpose, a further \gls{cli} application was created, which
enables the user to create and execute complex evaluation pipelines for
measurement data without programming. The example
\ref{Example_measurement_analysis_pipeline.png} shows a typical
measurement data analysis pipeline, which consists of the following
steps:

@@

In order to implement such a pipeline, the \emph{yaml} file format was
chosen for the definition of the pipeline, as this is for non
programmers to understand and can also be easily edited with a plain
text editor. Detailed examples can be found in the documentation
\cite{MagneticReadoutProcessingReadTheDocs}. The pipeline definition
consists of sections which execute the appropriate Python commands in
the background.

@@

During the development of the \gls{mrp}-library, test cases were also
created for all important functionalities and usecases. The test
framework \emph{PyTest} \cite{PyTest} was used for this purpose, as
it offers direct integration in most \gls{ide}s (see
\ref{MRP_library_test_results_for_different_submodules_executed_in_PyCharm_(+ide).png})
and also because it provides detailed and easy-to-understand test
reports as output in order to quickly identify and correct errors. It
also allows to tag tests, which is useful for grouping tests or
excluding certain tests in certain build environment scenarios. Since
all intended usecases were mapped using the test cases created, the code
of the test cases could later be used in slightly simplified variants
\ref{lst:pytest_example_code} as examples for the documentation.

@@

One important point that improves usability for users is the simple
installation of all \gls{mrp} modules. As it was created in the Python
programming language, there are several public package registry where
users can provide their software modules. Here, \emph{PyPi}
\cite{PyPI}
\ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png}
\cite{MagneticReadoutProcessingPyPI} is the most commonly used
package registry and offers direct support for the package installation
programm \gls{pip} \ref{lst:setup_lib_with_pip}.

@@

In order to provide comprehensive documentation for the enduser, the
source code was documented using Python-\emph{docstrings}
\cite{PythonDocstringReference} and the Python type annotations. The
use of type annotations also simplifies further development, as modern
\gls{ide}s can more reliably display possible methods to the user as an
assistance. \ref{lst:pydocstring}

@@

Since \emph{docstrings} only document the source code, but do not
provide simple how-to-use instructions, the documentation framework
\emph{Sphinx} \cite{SphinxDocumentation} was used for this purpose.
This framework makes it possible to generate \gls{html} or \gls{pdf}
documentation from various source code documentation formats, such as
the used \emph{docstrings}.

@@

For the hardware setup, the 3D-Fullsphere\ref{d-fullsphere} sensor was
used for the evaulation of the framework. As this is equipped with an
exchangeable magnetic holder mount, suitable holders are required for
the magnets to be measured. Ten random \emph{N45 12x12x12mm} neodymium
magnets were used, which are shown in figure
\ref{Ten_numbered_test_magnets_in_separate_holders.png}.

@@

The configured hardware was then connected to the host system using the
\emph{MRPcli config setupsensor}-\gls{cli} command. Afterwards, the
measurement was configured for an measurement run, using the following
configuration commands \ref{lst:evaluation_measurement_config}.

@@

The \emph{MRPcli measure run} command was then called up for each
individual magnet to execute a measurement. After each run, the
\emph{READING-NAME} parameter was filled with the id of the next magnet
so that all measurements could be assigned to the physical magnets.

@@

The next step for the user is the implementation of the filter algorithm
\ref{lst:custom_find_similar_values_algorithm}. This can have any
function signature and is implemented in the file
\emph{UDPPFunctionCollection.py}. This Python file is loaded when the
pipeline is started and all functions that are imported here as a module
or implemented directly can be called via the pipeline. As this is a
short algorithm, it was inserted directly into the file.

@@

The Python \emph{heapq} \cite{heapq} module, which implements a
priority queue, is used for this purpose. The calculated distances from
the \emph{CoG} value of the measurements to are inserted into this
queue. Subsequently, as many elements of the queue are returned as
defined by the \emph{IP\_return\_count} parameter. The actual sorting
was carried out by the queue in the background.

@@

On the right-hand side
\ref{MRP_evaluation_result_after_execution_of_the _user_defined_pipeline,_using_find_similar_values_algorithm.png},
the measured values are plotted as a result of the filter algorithm. As
the \emph{IP\_return\_count} parameter was set to four, only the four
most similar measurements were exported here. It can be seen from the
plotted \emph{CoG} \(\mu\)T deviation values, that these are closest to
an ideal Magnet with a CoG value of 0\(\mu\)T. This ideal value was
calculated with the function
\emph{MRP.MRPSimulation.generate\_simulated\_reading}, with the same
measurement parameters (magnet type, dimensions, sensor distance) as
they correspond to the mechanical structure of the used hardware sensor
\ref{d-fullsphere}.

@@

The filter algorithm implemented by the user was thus successfully
executed using the user-programmable pipeline. The calculation result
was successfully verified using raw measurement data and the final
result of the algorithm.

@@

In the previous chapter \emph{Usecase Evaluation}
\ref{usecase-evaluation} it was shown that the implementation of the
hardware and software framework for various magnetic field sensors was
successfully implemented.

In addition, the basic application by the user was demonstrated using an
example. This makes it possible to systematically characterise magnets
from the software and readout hardware side by means of data
acquisition, storage and analysis.

@@

For this evaluation, the sensors listed in the table
\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
were used for sensor characterisation. The additional column for the
\emph{Background-Noise} was taken from the respective data sheets of the
sesors and will be verified in the later \emph{Background-Noise}
measurement \ref{sensor-characterisation-background-noise}.

This selection was made for the following reasons:

The developed framework is directly compatible with a variety of
magnetic field sensors without modifications, including those listed in
the table. For this evaluation, the sensors listed in the table were
used for sensor characterisation. This selection was made for the
following reasons:

@@

The setup was placed and pre-wired in the temperature chamber 24 hours
before the series of measurements were carried out. The insulated
housing of a \emph{Voron 2.4} 3D printer, which has a separately
controlled internal heating system, was used as the temperature chamber.
To verify the temperature, an additional thermometer \emph{VC-7055BT}
was placed on the base plate. A 10mm thick \emph{PTFE} insulation plate
was placed between the floor and the sensor base plate to prevent direct
and uneven heating of the base plate by the heated floor.

The graphic
\ref{Sensor_evaluation_plattform_with_TLV493D_and MMC5603_sensors_placed_with_thermal_conductive_glue_on_an_aluminium_baseplate.png}
shows this basic setup, the \emph{Raspberry Pi Pico} shown here was used
as the readout hardware, on which the \emph{Unified Sensor Firmware} is
running. With additional connected switch, its possible to isolate or
select a sensor or both sensors to be queried from the firmware.

@@

For the software setup, \emph{MRPCli} \ref{command-line-interface} was
used to control and record the measurement series, with the functions of
the \emph{MRPDataVisualisation} \ref{mrpvisualisation} and
\emph{MRPAnalysis} \ref{mrpanalysis} packages from the library
\ref{software-readout-framework} being used for subsequent evaluation.
The recorded measurement series are automatically analysed using the
\emph{Programmable-Data Processing Pipeline}
\ref{programmable-data-processing-pipeline} and the results are
visualised.

@@

The procedure begins with the acquisition of the baseline by operating
the sensor without external magnetic fields. For this purpose, a sample
size of \emph{N=10000} measured values was recorded for the baseline
measurement.

@@

In the evaluation (see figure ), a linear function was also calculated
using curve fitting to determine the temperature coefficients of the
sensors. This makes it possible to calculate these deviations based on
the ambient temperature during the software calibration.

@@

>>>>

This makes it easy to integrate an own measuring devices into the
\gls{mrp} ecosystem at a later date. This is only possible with a
minimal functional hardware and firmware setup and was developed for
this purpose first.

@@

Each sensor that is loaded with the firmware, registeres on to the host
\gls{pc} as a serial interface. There are several ways for the user to
interact with the sensor:

@@

Two functional sensor platforms
\ref{Build_sensors_with_different_capabilities.csv} are built in order
to create a solid test platform for later tests and for the development
of the \gls{mrp} \ref{software-readout-framework}-library with the
previously developed sensor concepts.

@@

Since the \emph{MMC5603NJ} only has limited measurement range of total
\emph{6uT}, even small coin sized neodymium magnets already saturates
the sensor. It is possible to mount 3D printed spacers over the sensor
to increase the distance between the magnet and the sensor and thus also
measure these magnets.

@@

Another option is a custom interface board between the meter and the PC.
This is a good option as many modern \gls{pc}s or \gls{sbc}s no longer
offer an physical \emph{RS232} interface. As with the other sensors,
this interface consists of a \emph{Raspberry-Pi Pico} with an additional
level shifter.

The teslameter is connected to the microcontroller using two free
\gls{gpio}s in \gls{uart} mode. The firmware is adapted using a separate
build configuration. In order to be able to read and correctly interpret
the data from the microcontoller, the serial protocol of the sensor is
implemented in a customised version of the \emph{CustomSensor} class
\ref{lst:CustomSensorClass}.

@@

The software readout framework is the central software component that is
developed as part of this work. This software framework is intended to
provide a user-oriented data acquisition and analysis environment. For
this purpose, typical individual steps that occur in relation to these
tasks are implemented:

@@

All these possible task parts is divided into different blocks and users
is given the possibility of adding their own functionalities.

@@

For this purpose, the library is divided into individual modules, which
are shown in the graphic
\ref{MRP_library_module_high_level_overview.png}. In combination, these
represent a typical measurement-analysis-evaluation workflow of data.
For this purpose, a module system with standardised functional patterns
and data types is developed and packed together in a extendable Python
library.

@@

In order to realise the concept of user interaction points, the library
is divided into different modules. These modules can be divided into two
main categories:

@@

An important aspect is data import and export. On the one hand, this
allows the library to reuse and archive the measurements. On the other
hand, the focus during development is that it is also possible to use
the data in other programs.

@@

Taking these points into account, the \gls{json} format is chosen. This
is human and machine readable and there is a compatible parser for
almost every programming language.

The following code snippet \ref{lst:json_export_format_example} shows
the \gls{json} structure which is generated when a measurement thatt
using the library is exported. It can be seen that by using the
\gls{json} format, all measurement points and metadata are available in
readable plain text.

@@

To realize this, a \gls{lut} is created in the previous steps, which
contains information regarding \emph{requested capability}
-\textgreater{} \emph{sensor}-\gls{uuid} -\textgreater{} \emph{physical
sensor} and allows the commands to be routed.

@@

After generating simple measurements with random values in the previous
example \ref{mrpreading}, the next step is to record real sensor data.
For this purpose, the \emph{MRPHal} module is developed, which can
interact with all \emph{Unified Sensor} \ref{unified-sensor}-compatible
sensors. In the following example \ref{lst:mrpexample_hal}, an \emph{1D:
Single Sensor} \ref{d-single-sensor} is connected locally to the host
\gls{pc}.

@@

Although such examples are provided in the documentation, it must be
possible for programming beginners in particular to use them. To
simplify these tasks, a \gls{cli}
\ref{Example_measurement_analysis_pipeline.png} is implemented. The
libaray \gls{cli} implements the following functionalities:

@@

For this purpose, a further \gls{cli} application is created, which
enables the user to create and execute complex evaluation pipelines for
measurement data without programming. The example
\ref{Example_measurement_analysis_pipeline.png} shows a typical
measurement data analysis pipeline, which consists of the following
steps:

@@

In order to implement such a pipeline, the \emph{yaml} file format is
chosen for the definition of the pipeline, as this is for non
programmers to understand and can also be easily edited with a plain
text editor. Detailed examples can be found in the documentation
\cite{MagneticReadoutProcessingReadTheDocs}. The pipeline definition
consists of sections which execute the appropriate Python commands in
the background.

@@

During the development of the \gls{mrp}-library, test cases were also
created for all important functionalities and usecases. The test
framework \emph{PyTest} \cite{PyTest} is used for this purpose, as
it offers direct integration in most \gls{ide}s (see
\ref{MRP_library_test_results_for_different_submodules_executed_in_PyCharm_(+ide).png})
and also because it provides detailed and easy-to-understand test
reports as output in order to quickly identify and correct errors. It
also allows to tag tests, which is useful for grouping tests or
excluding certain tests in certain build environment scenarios. Since
all intended usecases were mapped using the test cases created, the code
of the test cases could later be used in slightly simplified variants
\ref{lst:pytest_example_code} as examples for the documentation.

@@

One important point that improves usability for users is the simple
installation of all \gls{mrp} modules. As it is created in the Python
programming language, there are several public package registry where
users can provide their software modules. Here, \emph{PyPi}
\cite{PyPI}
\ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png}
\cite{MagneticReadoutProcessingPyPI} is the most commonly used
package registry and offers direct support for the package installation
programm \gls{pip} \ref{lst:setup_lib_with_pip}.

@@

In order to provide comprehensive documentation for the enduser, the
source code is documented using Python-\emph{docstrings}
\cite{PythonDocstringReference} and the Python type annotations. The
use of type annotations also simplifies further development, as modern
\gls{ide}s can more reliably display possible methods to the user as an
assistance. \ref{lst:pydocstring}

@@

Since \emph{docstrings} only document the source code, but do not
provide simple how-to-use instructions, the documentation framework
\emph{Sphinx} \cite{SphinxDocumentation} is used for this purpose.
This framework makes it possible to generate \gls{html} or \gls{pdf}
documentation from various source code documentation formats, such as
the used \emph{docstrings}.

@@

For the hardware setup, the 3D-Fullsphere\ref{d-fullsphere} sensor is
used for the evaulation of the framework. As this is equipped with an
exchangeable magnetic holder mount, suitable holders are required for
the magnets to be measured. Ten random \emph{N45 12x12x12mm} neodymium
magnets were used, which are shown in figure
\ref{Ten_numbered_test_magnets_in_separate_holders.png}.

@@

The configured hardware is then connected to the host system using the
\emph{MRPcli config setupsensor}-\gls{cli} command. Afterwards, the
measurement is configured for an measurement run, using the following
configuration commands \ref{lst:evaluation_measurement_config}.

@@

The \emph{MRPcli measure run} command is then called up for each
individual magnet to execute a measurement. After each run, the
\emph{READING-NAME} parameter is filled with the id of the next magnet
so that all measurements could be assigned to the physical magnets.

@@

The next step for the user is the implementation of the filter algorithm
\ref{lst:custom_find_similar_values_algorithm}. This can have any
function signature and is implemented in the file
\emph{UDPPFunctionCollection.py}. This Python file is loaded when the
pipeline is started and all functions that are imported here as a module
or implemented directly can be called via the pipeline. As this is a
short algorithm, it is inserted directly into the file.

@@

The Python \emph{heapq} \cite{heapq} module, which implements a
priority queue, is used for this purpose. The calculated distances from
the \emph{CoG} value of the measurements to are inserted into this
queue. Subsequently, as many elements of the queue are returned as
defined by the \emph{IP\_return\_count} parameter. The actual sorting is
carried out by the queue in the background.

@@

On the right-hand side
\ref{MRP_evaluation_result_after_execution_of_the _user_defined_pipeline,_using_find_similar_values_algorithm.png},
the measured values are plotted as a result of the filter algorithm. As
the \emph{IP\_return\_count} parameter was set to four, only the four
most similar measurements were exported here. It can be seen from the
plotted \emph{CoG} \(\mu\)T deviation values, that these are closest to
an ideal Magnet with a CoG value of 0\(\mu\)T. This ideal value is
calculated with the function
\emph{MRP.MRPSimulation.generate\_simulated\_reading}, with the same
measurement parameters (magnet type, dimensions, sensor distance) as
they correspond to the mechanical structure of the used hardware sensor
\ref{d-fullsphere}.

@@

The filter algorithm implemented by the user is thus successfully
executed using the user-programmable pipeline. The calculation result
waiss successfully verified using raw measurement data and the final
result of the algorithm.

@@

In the previous chapter \emph{Usecase Evaluation}
\ref{usecase-evaluation} it is shown that the implementation of the
hardware and software framework for various magnetic field sensors is
successfully implemented.

In addition, the basic application by the user is demonstrated using an
example. This makes it possible to systematically characterise magnets
from the software and readout hardware side by means of data
acquisition, storage and analysis.

@@

For this evaluation, the sensors listed in the table
\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
were used for sensor characterisation. The additional column for the
\emph{Background-Noise} is taken from the respective data sheets of the
sesors and will be verified in the later \emph{Background-Noise}
measurement \ref{sensor-characterisation-background-noise}.

This selection is made for the following reasons:

The developed framework is directly compatible with a variety of
magnetic field sensors without modifications, including those listed in
the table. For this evaluation, the sensors listed in the table were
used for sensor characterisation. This selection is made for the
following reasons:

@@

The setup is placed and pre-wired in the temperature chamber 24 hours
before the series of measurements were carried out. The insulated
housing of a \emph{Voron 2.4} 3D printer, which has a separately
controlled internal heating system, is used as the temperature chamber.
To verify the temperature, an additional thermometer \emph{VC-7055BT} is
placed on the base plate. A 10mm thick \emph{PTFE} insulation plate is
placed between the floor and the sensor base plate to prevent direct and
uneven heating of the base plate by the heated floor.

The graphic
\ref{Sensor_evaluation_plattform_with_TLV493D_and MMC5603_sensors_placed_with_thermal_conductive_glue_on_an_aluminium_baseplate.png}
shows this basic setup, the \emph{Raspberry Pi Pico} shown here is used
as the readout hardware, on which the \emph{Unified Sensor Firmware} is
running. With additional connected switch, its possible to isolate or
select a sensor or both sensors to be queried from the firmware.

@@

For the software setup, \emph{MRPCli} \ref{command-line-interface} is
used to control and record the measurement series, with the functions of
the \emph{MRPDataVisualisation} \ref{mrpvisualisation} and
\emph{MRPAnalysis} \ref{mrpanalysis} packages from the library
\ref{software-readout-framework} being used for subsequent evaluation.
The recorded measurement series are automatically analysed using the
\emph{Programmable-Data Processing Pipeline}
\ref{programmable-data-processing-pipeline} and the results are
visualised.

@@

The procedure begins with the acquisition of the baseline by operating
the sensor without external magnetic fields. For this purpose, a sample
size of \emph{N=10000} measured values is recorded for the baseline
measurement.

@@

The graph of the \emph{TLV493d} is significantly steeper with a gradient
of \emph{-5.13 \(\mu\)T / \(^{\circ}\)C}, and it is also not as linear
as the \emph{MMC5603NJ}; there are clear jumps in the gradient. However,
the total change between the temperature regions of 175\(\mu\)T is less
than that of the \emph{MMC5603NJ} with 70\(\mu\)T, if the total
measurement range of the sensors is also taken into account.

In the evaluation (see figure
\ref{Sensor_temperature_sensitivity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}),
a linear function was also calculated using curve fitting to determine
the temperature coefficients of the sensors. This makes it possible to
compensate these deviations based on the ambient temperature during the
software calibration.

@@

Table \ref{Overview_of_all_characterised_sensor_properties.csv} shows a
summary of all recorded and analysed measured values of the two
characterised sensors \emph{TLV493D} and \emph{MMC5603NJ}. It can be
clearly seen that these differ significantly by a factor of \emph{x10}.
The \emph{TLV493D} performs seriously in the Senosr Noise measurement
and also performs worse than specified in the data sheet (98\(\mu\)T
instead of 175\(\mu\)T), but the large measuring range, which fulfils
the required specifications from chapter \emph{Research Question}
\ref{Research Question and Approach}, must be taken into account here,
which is not met by the \emph{MMC5603NJ}.
